Selecting and ranking interesting pairs of cyclic temporal granularities

### 2021-02-15 comparison_perm_scalar.Rmd
transformations episode

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      eval = TRUE,
                      warning = FALSE,
                      message = FALSE)
knitr::read_chunk("example_transformations.R")
library(tidyverse)
library(readr)
library(ggplot2)
```

@@

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      eval = TRUE,
                      warning = FALSE,
                      message = FALSE)
knitr::read_chunk("example_transformations.R")
library(tidyverse)
library(readr)
library(ggplot2)
library(here)
```

@@

```{r wpd-permutation-d, fig.cap = " The distribution of $wpd_{permutation}$ is plotted. The distributions are more similar across different nx and nfacet (specially for small nx and nfacet) but this approach has the downside of more computational time."}

@@

- the two approaches permutation and modelling could be brought to the same scale so that for smaller categories, permutation could be done and for larger categories, stick to modelling approach

## bringing both to the same scale also helps means you have a lower and upper bound for the normalised wpd

```{r dist-new-same-scale}

G21 <- read_csv("simulations/raw/null_design_quantrans/data-agg/all_data_wpd_N01.csv")

beta_lm2 <- lm(actual ~ log(`nx * nfacet`), data = G21_median)

beta_lm2 <- lm(actual ~ log(`nx * nfacet`), data = G21_median)

G21 %>% 
  ggplot(aes(x=log(nx*nfacet), y = (value - intercept -slope*log(nx*nfacet)))) +
  geom_point() + stat_summary(fun=mean, geom="line", aes(group=1), color = "blue") + 
  xlab("$wpd_norm =  wpd_raw - slope*log(nx*nfacet)$")

G21_model_data <- G21 %>% 
  mutate(model =
           (value - intercept - 0.0027*log(nx*nfacet))/0.0027
         ) %>% 
  mutate(model_trans = 
           (model - min(model))/(max(model) - min(model)))

G21_model_data$model %>% summary()
G21_model_data$model_trans %>% summary()

G21_perm_data <- G21_permutation %>% 
  mutate(perm_trans =
           (
             (wpd_permutation - min(wpd_permutation))/
                (
                  max(wpd_permutation) - min(wpd_permutation)
                )
             )
           )

G21_all_data <- G21_model_data %>% 
  left_join(G21_perm_data, by = c("nx", "nfacet", "perm_id")) %>% 
  pivot_longer(cols = c(6,8),
               names_to = "type_estimate",
               values_to = "value_estimate")

G21_all_data %>% 
  ggplot() +
  geom_density(aes(x = value_estimate, 
                   fill = type_estimate), 
               alpha = 0.7) +
  facet_grid(nx~nfacet,
             labeller = "label_both") +
  theme(legend.position = "bottom") +
  scale_fill_manual(values = c("#0072B2", "#CC79A7")) +
  xlab("wpd_norm2")
```

G21_perm_data %>% 
    ggplot() +
  geom_density(aes(x = perm_trans), 
                   fill = "blue") +
  facet_grid(nx~nfacet,
             labeller = "label_both") +
  theme(legend.position = "bottom") 
```

# bringing both to same scale

- the two approaches permutation and modelling could be brought to the same scale so that for smaller categories, permutation could be done and for larger categories, stick to modelling approach

## bringing both to the same scale also helps means you have a lower and upper bound for the normalised wpd

# the following looks right where the $wpd_{norm}$ are just plotted like that and the model is GLM with distribution Gamma and link-function inverse

```{r dist-new-same-scale-link}

G21 <- read_csv("simulations/raw/null_design_quantrans/data-agg/all_data_wpd_N01.csv")

# fit model median to log(nx*nfacet)
# fit_lm2 <- lm(actual ~ poly(log(`nx * nfacet`) ,1, raw=TRUE), data = G21_median)
# 
# summary(fit_lm2)

glm_fit <- glm(actual ~ log(`nx * nfacet`),
              family = Gamma(link = "inverse"),
              data = G21_median)

summary(glm_fit)

intercept <- glm_fit$coefficients[1]
slope <- glm_fit$coefficients[2]

G21 %>% 
  ggplot(aes(x=log(nx*nfacet),
             y = ((1/value)
                  - intercept - 
                    slope*log(nx*nfacet))/slope)) +
  geom_point() + stat_summary(fun=mean, geom="line", aes(group=1), color = "blue")

G21_model_data <- G21 %>% 
  mutate(model =
           ((1/value)
                  - intercept - 
                    slope*log(nx*nfacet))/slope) %>% 
  mutate(model_trans = 
           (model - mean(model))/sd(model))

G21_model_data$model %>% summary()

G21_perm_data <- G21_permutation %>% 
  mutate(perm_trans =
           (
             (wpd_permutation - min(wpd_permutation))/
                (
                  max(wpd_permutation) - min(wpd_permutation)
                )
             )
           )

G21_all_data <- G21_model_data %>% 
  left_join(G21_perm_data, by = c("nx", "nfacet", "perm_id")) %>% 
  pivot_longer(cols = c(6,7),
               names_to = "type_estimate",
               values_to = "value_estimate")

G21_all_data %>% 
  ggplot() +
  geom_density(aes(x = value_estimate, 
                   fill = type_estimate), 
               alpha = 0.7) +
  facet_grid(nx~nfacet,
             labeller = "label_both") +
  theme(legend.position = "bottom") +
  scale_fill_manual(values = c("#CC79A7", "#0072B2")) +
  xlab("wpd_norm2")

# are scales same

G21_model_data %>%
  group_by(nx, nfacet) %>% 
  summarise(sd_model = sd(model))

### 2021-02-15 paper/main.Rmd
transformations episode

>>>>

```{r}
all_data_scalar <- read_rds(here("paper/sim_table/all_data_scalar.rds"))
all_data <- read_rds(here("paper/sim_table/all_data.rds"))

merged_data <- left_join(all_data_scalar,all_data, by = c("customer_id",
                                                          "facet_variable",
                                                          "x_variable")) %>% 
  rename("wpd_scalar"  = "wpd_norm.x",
         "wpd_perm" = "wpd_norm.y")

merged_data %>% 
  mutate(pair = paste(facet_variable, x_variable, sep = "-")) %>% 
  ggplot() +
  geom_point(aes(x = wpd_scalar, y = wpd_perm, color = pair, group = pair))
  #geom_point(aes(x = wpd_scalar, y = wpd_perm, alpha = 0.05))
